
\chapter{Introduction}

AutoML (Automated Machine Learning) is becoming a new challenge for the industry, aiming to reshape the way business and individuals would use machine learning in their everyday life. This process is an automation of routine work of ML engineers and contains of problems industry regularly solves, including but not limited to data preparation, feature engineering, feature extraction, neural architecture search, hyperparameters selection etc.

As machine learning provides endless variety of automation possibilities for industries the problem of automation of ML industry itself seems natural. However, it is much trickier because the domain itself is developing rapidly. For decades ML engineers was pioneers in the new era of computer science research. As a result a new industry was shaped and this industry requires automation.

We believe that world would benefit from democratization of this new tools.
ML is becoming a part of everyday routine for thousands of developers worldwide providing with ability to run models even on portable devices, IoT chips and other mass market hardware. AutoML is a big move towards in terms of variety of different applications created, tools used and research possibilities.

AutoML become a natural product for almost all big technological companies. Google, Amazon, Salesforce and others are offering AutoML products that allows non-experts to create their own ML solutions.

Still, existing AutoML techniques requires lots of computational resources and most of the research in the field is covered by tech giants nowadays. 

We think that a task of neural architecture search should be optimized. We are using probabilistic approaches to show that they are able to handle an exploration and exploitation problem efficiently for reinforcement learning agents which are solving neural architecture search problems.

We are focusing on neural architecture search problem, especially on hyperparameter optimization task because historically this problem is solved mainly using exhaustive search techniques, such as grid search. Engineers often follows their empirical knowledge and try to guess optimal parameters to tune models. It is hard to optimize and automate something without knowing the nature behind it - so we are working on more effective approach than exhaustive search.

We are using reinforcement learning paradigm since it is performing well solving NAS problems. \cite[See][]{ZophL16}

\section{History}



\endinput